Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-11-24 src/tex/ms.tex
update

\section{Introduction}
\label{sec:Introduction}
% Motivation
Since Einstein proposed his theory of general relativity (GR), it was tested in
a wide range of length scales. After a century, we know that GR does not agree
with quantum theories at some length scale. To unify both theories, we need to
study the possibility of different beyond-GR theories. \kw{I think now it kind
of goes into birefringence too fast. Maybe talk about what effect one may expect
to see in GW in general a bit?} Some beyond-GR theories such as Chern-Simons
gravity suggests that there is gravitational wave (GW) amplitude birefringence,
while GR predicts there is no birefringence. GW amplitude birefringence is a
property of space-time which consists of the enhancement of one GW polarization
over the other during the propagation of the wave. the local modification of the
amplitude is small, but it grows with the number of cycles the GW is propagated.

@@

% What's new?
In this paper, we used a birefringence model with higher order terms which
include the frequency dependence of amplitude birefringence to perform a more
accurate parameter estimation (PE). We also performed Bayesian inference on
events in GWTC-3, the third GW transient catalog. We included 69 binary black
hole merger events with smallest false alarm rate $\leq1\mathrm{yr^{-1}}$. These
events are also listed in TABLE I in
\citet{GWTC_3_population}.\footnote{GW190720 and GW200129 are included in the
list in \citet{GWTC_3_population}, but we did not include them in this study.
Details in Discussion.}

>>>>

\section{Introduction}
\label{sec:Introduction}
% Motivation
Since Einstein proposed his theory of general relativity (GR), it was tested in
a wide range of length scales. After a century, we know that GR does not agree
with quantum theories at some length scale. To unify both theories, we need to
study the possibility of different beyond-GR theories. \kw{I think now it kind
of goes into birefringence too fast. Maybe talk about what effect one may expect
to see in GW in general a bit? Say there is polarization modification, phasing
modification, etc.} Some beyond-GR theories such as Chern-Simons gravity
suggests that there is gravitational wave (GW) amplitude birefringence, while GR
predicts there is no birefringence. GW amplitude birefringence is a property of
space-time which consists of the enhancement of one GW polarization over the
other during the propagation of the wave. the local modification of the
amplitude is small, but it grows with the number of cycles the GW is propagated.

@@

% What's new?
In this paper, we used a birefringence model with higher order terms which
include the frequency dependence of amplitude birefringence to perform a more
accurate parameter estimation (PE) \kw{I think there is qualitative difference
between this work and former works, so it is not just more accurate}. We also
performed Bayesian inference on events in GWTC-3, the third GW transient
catalog. We included 69 binary black hole merger events with smallest false
alarm rate $\leq1\mathrm{yr^{-1}}$. These events are also listed in TABLE I in
\citet{GWTC_3_population}.\footnote{GW190720 and GW200129 are included in the
list in \citet{GWTC_3_population}, but we did not include them in this study.
Details in Discussion.}
